### 2012-09-04 inst/examples/figure3.Rmd
smoothed plot uses first order spline, #26

ggplot(policy) + geom_point(aes(stock, stock-x_grid[value], color=variable))
dat <- subset(policy, stock < 140)
dt <- data.table(dat)
linear <- dt[,approx(stock, stock-x_grid[value], xout=seq(1,150, length=15)), by=variable]
ggplot(linear) + geom_smooth(aes(x,y,color=variable), fill=NA) + xlab("Measured Stock") + ylab("Optimal Expected Escapement")
#  geom_point(aes(stock, stock-x_grid[value], color=variable)) +
# geom_smooth(aes(stock, stock-x_grid[value], color=variable)) 
```

>>>>

ggplot(policy) + geom_point(aes(stock, stock-x_grid[value], color=variable), shape="+")
dat <- subset(policy, stock < 140)
dt <- data.table(dat)
linear <- dt[,approx(stock, stock-x_grid[value], xout=seq(1,150, length=15)), by=variable]
ggplot(linear) + 
	stat_smooth(aes(x,y,color=variable), degree=1, se=FALSE, span=.3) + 
	xlab("Measured Stock") + ylab("Optimal Expected Escapement")
```
